---
title: "CompilingCHLIntegrated"
author: "DennieT"
date: "2022-11-16"
output: html_document
---


#Import package
```{r}
library("tidyverse")
library(ggplot2)
library("lubridate")
library(dplyr)

library('pracma')
library("tidyverse")
```


```{r, echo = FALSE}
library(kableExtra)
```


#Set Directory
```{r}
getwd()
setwd("C:/Users/denni/Documents/RStudioBigelow/FieldProject")
```



#Import Data
```{r}
CHLIntegrateData <- read.csv("DaRTS2012_2022CTD.csv", header=TRUE)
#View(CHLIntegrateData)

CHLIntegrateData <- CHLIntegrateData %>% mutate(Date = mdy(CHLIntegrateData$Date))

ZooplanktonData2 <- read.csv("ZooplanktonData2.csv", header=TRUE)

ZooplanktonData2 <- ZooplanktonData2 %>% mutate(Date = ymd(ZooplanktonData2$Date))
#View(ZooplanktonData2)
```



#Filter data & Integrate 2012-09-11 Station 1 data
```{r}
#Combine filter
CHL09112012A <- dplyr::filter(CHLIntegrateData, Station == 1 & Year == 2012 & Month == 9 & Day == 11)
#View(CHL2012)

fluorescence09112012A <- CHL09112012A$Fluorescence_mg_m3
depth09112012A <- CHL09112012A$Depth_m

x09112012A=trapz(depth09112012A,fluorescence09112012A)
x09112012A
```



#Filter data  & Integrate 2012-09-11 Station 3 data
```{r}
#Combine filter
CHL09112012C <- dplyr::filter(CHLIntegrateData, Station == 3 & Year == 2012 & Month == 9 & Day == 11)
#View(CHL2012)

fluorescence09112012C <- CHL09112012C$Fluorescence_mg_m3
depth09112012C <- CHL09112012C$Depth_m

x09112012C=trapz(depth09112012C,fluorescence09112012C)
x09112012C

#Use cumtrapz if you want added area for each trapezoid
#x09112012C=cumtrapz(depth09112012C,fluorescence09112012C)
```

#Filter data  & Integrate 2012-09-11 Station 4 data
```{r}
#Combine filter
CHL09112012D <- dplyr::filter(CHLIntegrateData, Station == 4 & Year == 2012 & Month == 9 & Day == 11)
#View(CHL2012)

fluorescence09112012D <- CHL09112012D$Fluorescence_mg_m3
depth09112012D <- CHL09112012D$Depth_m

x09112012D=trapz(depth09112012D,fluorescence09112012D)
x09112012D
```


#Filter data & Integrate 2012-09-18 Station 1 data
```{r}
#Combine filter
CHL09182012A <- dplyr::filter(CHLIntegrateData, Station == 1 & Year == 2012 & Month == 9 & Day == 18)
#View(CHL09182012A

fluorescence09182012A <- CHL09182012A$Fluorescence_mg_m3
depth09182012A <- CHL09182012A$Depth_m

x09182012A=trapz(depth09182012A,fluorescence09182012A)
x09182012A
```



# Get Fluorescence for all water columns
```{r}
fluorescence <- CHLIntegrateData$Fluorescence_mg_m3
depth <- CHLIntegrateData$Depth_m
Station <- CHLIntegrateData$Station
Date <- CHLIntegrateData$Date
typeof(CHLIntegrateData$Date)

#extract good values
nonans <- is.finite(fluorescence)

Fluorescencenonan <- fluorescence[nonans]
Depthnonan <- depth[nonans]
Station <- Station[nonans]
Date <- Date[nonans]


#create dataframe
nonandata <- data.frame(Date, Station, Depthnonan, Fluorescencenonan)

#Mutate add new column to a dataframe
#nonandata <- mutate(nonandata, Date = ymd(nonandata$Date))

#apply trapz function
trapzdata <- nonandata %>% 
  group_by(Date, Station) %>% 
  summarise(IntegratedCHL=trapz(Depthnonan,Fluorescencenonan))
#trapzdata
```


#Get mean of Temperature at depth 2 (1.5 to 2.5 meters)
```{r}
Temp_2m <- CHLIntegrateData %>%  filter(Depth_m >= 1.5 & Depth_m <= 2.5)%>% 
  group_by(Date, Station) %>% 
  summarize_all(mean)

#Temp_2m <- Temp_2m %>% mutate(Date = ymd(Temp_2m$Date)) #Change format to Date type

Tempfilter1 <- data.frame(Date=Temp_2m$Date, Station=Temp_2m$Station, Temperature_2m=Temp_2m$Temperature_C)
```



#Get mean of Temperature at depth 10 (9.5 to 10.5 meters)
```{r}
Temp_10m <- CHLIntegrateData %>%  filter(Depth_m >= 9.5 & Depth_m <= 10.5)%>% 
  group_by(Date, Station) %>% 
  summarize_all(mean)
#Temp_10m <- Temp_10m %>% mutate(Date = ymd(Temp_10m$Date))

Tempfilter2 <- data.frame(Date=Temp_10m$Date, Station=Temp_10m$Station, Temperature_10m=Temp_10m$Temperature_C)
```



#Get mean of CHL at depth 2 (1.5 to 2.5 meters)
```{r}
CHL_2m <- CHLIntegrateData %>%  filter(Depth_m >= 1.5 & Depth_m <= 2.5)%>% 
  group_by(Date, Station) %>% 
  summarize_all(mean)
#CHL_2m <- CHL_2m %>% mutate(Date = ymd(CHL_2m$Date))

Tempfilter3 <- data.frame(Date=CHL_2m$Date, Station=CHL_2m$Station, Chlorophyll_2m=CHL_2m$Fluorescence_mg_m3)
```



#Get mean of CHL at depth 10 (9.5 to 10.5 meters)
```{r}
CHL_10m <- CHLIntegrateData %>%  filter(Depth_m >= 9.5 & Depth_m <= 10.5)%>% 
  group_by(Date, Station) %>% 
  summarize_all(mean)
#CHL_10m <- CHL_10m %>% mutate(Date = ymd(CHL_10m$Date))

Tempfilter4 <- data.frame(Date=CHL_10m$Date, Station=CHL_10m$Station, Chlorophyll_10m=CHL_10m$Fluorescence_mg_m3)
```


#Get CHL max
```{r}
# CHLIntegrateData <- CHLIntegrateData %>% mutate(Depth = round(CHLIntegrateData$Depth_m))
# nonans <- is.finite(CHLIntegrateData$Fluorescence_mg_m3)
# Fluorescence_mg_m3 <- CHLIntegrateData$Fluorescence_mg_m3[nonans]
# Date <- CHLIntegrateData$Date[nonans]
# Station <- CHLIntegrateData$Station[nonans]
# Temperature_C <- CHLIntegrateData$Temperature_C[nonans]
# 
# CHLMax <- data.frame(Date, Station, Fluorescence_mg_m3, Temperature_C)
# CHLMax <- CHLMax %>% 
#   group_by(Date, Station) %>% 
#   CHLMax$Fluorescence_mg_m3[apply(CHLMax,2,which.max)]
#    # summarise(CHLMax = max(Fluorescence_mg_m3, na.rm=TRUE), Temp_CHLMax = maxFluorescence_mg_m3, na.rm=TRUE)Temperature_C)

```


#Joining all the dataframe
```{r}
ZooplanktonData3 <- ZooplanktonData2 %>%
  full_join(trapzdata)

ZooplanktonData4 <- ZooplanktonData3 %>%
  full_join(Tempfilter1) %>%
  full_join(Tempfilter2) %>%
  full_join(Tempfilter3) %>%
  full_join(Tempfilter4)

#save to csv
write.csv(ZooplanktonData3,"ZooplanktonData3.csv", row.names=FALSE)
write.csv(ZooplanktonData4,"ZooplanktonData4.csv", row.names=FALSE)
```


